% LaTeX file for resume
% This file uses the resume document class (res.cls)
% Adrien Thebo
% Sun Jan 23 22:07:44 PST 2011

\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page
\usepackage{multicol}
\usepackage{url}

%\setlength{\topmargin}{-0.4in}
%\linespread{0.95}
%\setlength{\oddsidemargin}{-0.4in}
%\setlength{\evensidemargin}{-0.4in}
\usepackage{simplemargins}
\settopmargin{0.5in}
\setbottommargin{0.1in}

\begin{document}

\name{Adrien Thebo\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name

\address{\bf  ADDRESS\\
    2130 S.W. Camelot Court \#11\\
    Portland, Oregon, 97225\\
    (208) - 860 - 8702\\
}

\begin{resume}

\vspace{-0.2in}

\section{OBJECTIVE}
To work in the information technology industry, doing development and systems
administration to produce and maintain secure, effective, and highly functional
networks.

\vspace{-0.1in}
\section{QUALIFICATIONS}
\vspace{-0.2in}
\subsection{Operating Systems}
\vspace{-0.2in}
\begin{multicols}{3}
  \begin{itemize}
    \item Windows Server 2003
    \item Windows XP
    \item Windows 7
    \item Gentoo Linux
    \item Ubuntu Linux
    \item Fedora Linux
    \item CentOS Linux
    \item FreeBSD
    \item Solaris
  \end{itemize}
\end{multicols}

\vspace{-0.5in}
\subsection{Languages}
\vspace{-0.2in}

\begin{multicols}{4}
  \begin{itemize}
    \item C
    \item C++
    \item x86 assembly
    \item Java
    \item Groovy
    \item Perl
    \item Python
    \item Ruby
    \item PHP
    \item Bash
    \item SQL
    \item XML
    \item HTML
    \item CSS
    \item Javascript
    \item \LaTeXe
  \end{itemize}
\end{multicols}

\vspace{-0.25in}

\section{EXPERIENCE}
  \vspace{-0.1in}
  \begin{tabbing}
  \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
  {\bf Unix Systems Administrator} \>Computer Action Team, \>Fall 2009 - Present\\
			   \>Portland, OR
  \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
  Maintained and upgraded server, client, and network infrastructure, configured
  and maintained system software. Worked extensively with students and faculty to
  provide for their computing needs.

  \vspace{-0.21in}

  \begin{tabbing}
  \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
  {\bf Contract Web Development} \>Immigration Legal Clinic\> Winter 2009\\
			\>Boulder, Colorado
  \end{tabbing}\vspace{-20pt}
  Used Groovy and Grails to create custom client tracking web application.
  Worked under open source license, and code is freely available at
  \url{http://code.google.com/p/ilcdb}

  \vspace{-0.21in}

  \begin{tabbing}%
  \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
  {\bf Threat Prevention Team}  \>eSoft Incorporated \> Summer 2007, 2008\\
			\>Broomfield, Colorado
  \end{tabbing}\vspace{-20pt}
  Implemented significant parts of a realtime blackhole list system based
  against spammers, Codeveloped a log parser and aggregator with an ExtJS
  based webconsole. Wrote extensive URL collection and spirdering
  scripts for the Sitefilter product.

  \vspace{-0.21in}

  \begin{tabbing}%
  \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
  {\bf Systems Administrator} \>Quantum Point Technologies\> 2005 - 2006\\
			\>Boise, Idaho
  \end{tabbing}\vspace{-20pt}
  Performed on-demand work for small businesses, including network hardware
  configuration, and server and client configuration and maintenace.

\vspace{-0.1in}

\section{EDUCATION}
  Portland State University, Portland, Oregon \\
  Current degree program in Computer Science, 2009 - current \\
  \vspace{-0.5in}
  \subsubsection{Projects}
  \vspace{-0.2in}
    Rebuilt the Computer Science department website in Ruby on Rails, deployed
    issue tracking software and converted the project to Git. Available at \url{cs.pdx.edu}

  \vspace{-0.2in}
  Colorado State University, Fort Collins, CO \\
  Classes in Computer Science/Applied Computing Technology, 2006 - 2008 \\
  \vspace{-0.5in}
  \subsubsection{Projects}
  \vspace{-0.2in}
    Performed research in speech recognition systems on robots, to make
    remotely controllable systems. Also participated in research on Biomimetic
    vision, tuning the visual error correction systems.

\vspace{-0.1in}
\section{EXTRACURRICULAR ACTIVITIES}
    Chair of the Association for Computing Machinery, PSU Chapter, January - May 2010 \\
    ACM tutor, Fall 2009 \\
    Fourth Place at NetSec Capture the Flag competition with the Air Force Academy, 2007 \\
    Two time silver medalist in Internetworking, SkillsUSA Idaho state competition 2005, 2006 \\

\end{resume}
\end{document}
